---
title: "Project Test"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE,
                      fig.width = 4, fig.height = 3)
```


Load this:

```{r}
## Load libraries
if(!require(tidyverse)) {install.packages("tidyverse"); require(tidyverse)}
#if(!require(rstudioapi)) {install.packages("rstudioapi"); require(rstudioapi)}
if(!require(MPsychoR)) {install.packages("MPsychoR"); require(MPsychoR)}
if(!require(sjPlot)) {install.packages("sjPlot"); require(sjPlot)}
if(!require(lme4)) {install.packages("lme4"); require(lme4)}
if(!require(lmerTest)) {install.packages("lmerTest"); require(lmerTest)}
if(!require(languageR)) {install.packages("languageR"); require(languageR)}

if (!requireNamespace("MCMCglmm", quietly = TRUE)) {
  install.packages("MCMCglmm")
}

library(MCMCglmm)
## Set plotting preferences
ggplot2::theme_set(ggplot2::theme_bw(base_size=18))
ggplot2::theme_update(panel.grid = ggplot2::element_blank(), 
                      strip.background = ggplot2::element_blank(),
                      legend.key = ggplot2::element_blank(),
                      panel.border = ggplot2::element_blank(),
                      axis.line = ggplot2::element_line(),
                      strip.text = ggplot2::element_text(face = "bold"),
                      plot.title = element_text(hjust = 0.5))
options(ggplot2.discrete.colour= c("#A31F34", "#8A8B8C"))


## Set function defaults
filter <- dplyr::filter
group_by <- dplyr::group_by
summarize <- dplyr::summarize
select <- dplyr::select

## Set working directory
#setwd(dirname(rstudioapi::getActiveDocumentContext()$`path`))
```

First, load the data and filter out the filler conditions:

```{r}
## Load data
replication <- read.csv("9.59_Replication_80_participants.csv", header = TRUE, sep = ",")
#low_noise <- read.csv("40_participants_real_data.csv", header = TRUE, sep = ",")
high_noise<- read.csv("Pip_Extension_high_noise_45_participants.csv", header = TRUE, sep = ",")


#Add column for expected_noise
#arial_data <- arial_data %>% mutate(font = "arial")
replication <- replication %>% mutate(expected_noise = "null")
high_noise <- high_noise %>% mutate(expected_noise = "high")


#Remove "any_question" column from high_noise 
high_noise <- subset(high_noise, select = -any_questions)


```
```{r}
#Combine arial and comic into one dataframe
#data <- rbind(arial_data, comic_data)
data <- rbind(high_noise, replication)


#Remove cond filler
data <- data %>% filter(cond != "filler")
#Remove conds that contain active or passive
data <- data %>% filter(!grepl("active", cond))
data <- data %>% filter(!grepl("passive", cond))

```

Group data two different ways:
- cond that contains "do" or "po"
- cond that contains "implausible" or "plausible"

And add literal response as a variable.

```{r}
#Create variable for cond that contains "do" or "po"
data <- data %>% 
  mutate(do_po = ifelse(grepl("DO", cond), "DO", "PO")) %>% #Create factor
  mutate(do_po = factor(do_po, levels = c("DO", "PO"))) #Set factor levels
#Create variable for cond that contains "implausible" or "plausible"
data <- data %>% 
  mutate(plausibility = ifelse(grepl("implausible", cond), "implausible", "plausible")) %>% #Create factor
  mutate(plausibility = factor(plausibility, levels = c("implausible", "plausible"))) #Set factor levels

#Response is literal if literal_response = response
data <- data %>% 
  mutate(is_literal = ifelse(response == literal_response, "literal", "nonliteral")) %>% #Create factor
  mutate(is_literal = factor(is_literal, levels = c("nonliteral", "literal"))) #Set factor levels
```

We look at the literal rate for each participant_id, so we can filter out those with a literal rate below .75 for plausible data:

```{r}
#Group by participant_id
plausible_participant_grouped_data <- data %>% #Only look at plausible
  filter(plausibility == "plausible") %>%
  group_by(participant_id) %>%
  summarize( #Get literal response rate for each condition, and calculate confidence intervals
    literal_response_rate = mean(is_literal == "literal"),
    n = n(),
    ci = 1.96 * sqrt(literal_response_rate * (1 - literal_response_rate) / n)
  )

plausible_participant_grouped_data

#For "data": filter out participants with literal rate below .75 for "plausible_data"
ppgd <- plausible_participant_grouped_data
data <- data %>% #Filter out data with low plausibile literal response rate: assumed to not be reading as accurately
  filter(participant_id %in% ppgd$participant_id[ppgd$literal_response_rate >= .75])

```

Next: get literal rates sorted by do vs. po and implausible vs. plausible at the same time

```{r}

#Show literal response rate for do vs. po, implausible vs. plausible, and font
both_literal <- data %>%
  group_by(do_po, plausibility, expected_noise) %>%
  summarize( #Get literal response rate for each condition, and calculate confidence intervals
    literal_response_rate = mean(is_literal == "literal"),
    n = n(),
    ci = 1.96 * sqrt(literal_response_rate * (1 - literal_response_rate) / n)
  )

```

Then, we plot the combination.

```{r}
#Plot literal response rate for do vs. po and implausible vs. plausible, create a separate plot for each expected_noise
ggplot(both_literal, aes(x = do_po, y = literal_response_rate, fill = plausibility)) + # <- Add fill = plausibility
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~expected_noise) +
  scale_fill_manual(values = c("#A31F34", "#8A8B8C")) +
  scale_x_discrete(labels = c("do", "po")) +
  scale_y_continuous(limits = c(0, 1)) +
  labs(x = "Condition", y = "Literal response rate", fill = "Plausibility") +
  theme(legend.position = "bottom")
```
```

Filter out plausible data, and plot the literal response rate for do vs. po.

```{r}
#Filter out plausible data
implausible_data <- data %>% filter(plausibility == "implausible")
noisy_data <- data %>% filter(expected_noise != "null" )
replication_data <- data %>% filter(expected_noise == "null" )
#Get literal response rate for do vs. po, with ci
dopo_literal <- noisy_data %>% 
  group_by(do_po, expected_noise) %>% 
  summarize( #Get literal response rate for each condition, and calculate confidence intervals
    literal_response_rate = mean(is_literal == "literal"),
    n = n(),
    ci = 1.96 * sqrt(literal_response_rate * (1 - literal_response_rate) / n)
  )

  dopo_literal_repli <- replication_data %>% 
  group_by(do_po, expected_noise) %>% 
  summarize( #Get literal response rate for each condition, and calculate confidence intervals
    literal_response_rate = mean(is_literal == "literal"),
    n = n(),
    ci = 1.96 * sqrt(literal_response_rate * (1 - literal_response_rate) / n)
  )
```

For the replication:
```{r}

ggplot(dopo_literal_repli, aes(x = do_po, y = literal_response_rate, fill = do_po)) + # <- Add fill = do_po
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("DO" = "#A31F34", "PO" = "#8A8B8C")) +
  labs(x = "Condition", y = "Literal Response Rate", title = "Literal Response Rate by Condition") +
  scale_y_continuous(limits = c(0, 1)) +
  theme(
  plot.title = element_text(hjust = 0.5, size = 40),
  axis.title.x = element_text(size = 26),
  axis.title.y = element_text(size = 26),
  axis.text.x = element_text(size = 36),
  axis.text.y = element_text(size = 24),
  legend.text = element_text(size = 36),
  legend.title = element_text(size = 36))+
  geom_errorbar(aes(ymin = literal_response_rate - ci, ymax = literal_response_rate + ci), width = .2, position = position_dodge(.9))
```

And for the extension:

```{r}
#Plot literal response rate for do is red, po is grey
ggplot(dopo_literal, aes(x = do_po, y = literal_response_rate, fill = do_po)) + # <- Add fill = do_po
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("DO" = "#A31F34", "PO" = "#8A8B8C")) +
  labs(x = "Condition", y = "Literal Response Rate", title = "Literal Response Rate by Condition") +
  scale_y_continuous(limits = c(0, 1)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~font) +
  theme(
  plot.title = element_text(hjust = 0.5, size = 40),
  axis.title.x = element_text(size = 26),
  axis.title.y = element_text(size = 26),
  axis.text.x = element_text(size = 36),
  axis.text.y = element_text(size = 24),
  legend.text = element_text(size = 36),
  legend.title = element_text(size = 36),
  panel.spacing.x = unit(5, "lines"),
  strip.text = element_text(size = 30))+
  geom_errorbar(aes(ymin = literal_response_rate - ci, ymax = literal_response_rate + ci), width = .2, position = position_dodge(.9))
```

Next, run a logistic regression on the data to see if the difference between do and po is significant.

We'll restrict our scope to implausible data, since we're interested in the effect of do vs. po on literal response rate.

Set model for arial only:
```{r}
#Filter implausible_data by arial
implausible_data_arial <- implausible_data %>% filter(font == "arial")

prior <- list(G = list(G1 = list(V = 1e+06, nu = 0.002),
                       G2 = list(V = 1e+06, nu = 0.002)))

# Fit the Bayesian mixed-effects model using MCMC
mcmcglmm_model <- MCMCglmm(is_literal ~ do_po,
                           random = ~ item + participant_id, #Includes both slopes and intercepts
                           family = "categorical",
                           data = implausible_data_arial,
                           prior = prior,
                           nitt = 100000,  # Number of MCMC iterations
                           thin = 10,     # Thinning interval
                           verbose = FALSE)

summary(mcmcglmm_model)
```
```{r}


# Set up an uninformative prior
prior <- list(G = list(G1 = list(V = 1e+06, nu = 0.002),
                       G2 = list(V = 1e+06, nu = 0.002)))


# Fit the Bayesian mixed-effects model using MCMC
mcmcglmm_model <- MCMCglmm(is_literal ~ do_po * font,
                           random = ~ item + participant_id, #Includes both slopes and intercepts
                           family = "categorical",
                           data = implausible_data,
                           prior = prior,
                           nitt = 100000,  # Number of MCMC iterations
                           thin = 10,     # Thinning interval
                           verbose = FALSE)

# Show results
summary(mcmcglmm_model)
```



Creating a simple dataset with one data point in each condition: 
Cross between stimulus category (face vs. object) and emotional contents (neutral vs. emotional)
```{r}
#Create dataset
data <- data.frame(
  stimulus_category = c("face", "face", "object", "object"),
  emotional_content = c("neutral", "emotional", "neutral", "emotional"),
  response = c(.5, .7, .6, .95)
)

#Group by stimulus category and emotional content
data <- data %>%
  group_by(stimulus_category, emotional_content) %>%
  summarize( #Get literal response rate for each condition, and calculate confidence intervals
    activation_magnitude = mean(response),
  )

#Plot literal response rate for both conditions
ggplot(data, aes(x = stimulus_category, y = activation_magnitude, fill = emotional_content)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("emotional" = "#A31F34", "neutral" = "#8A8B8C")) +
  labs(x = "Stimulus Category", y = "Activation Magnitude", title = "Activation by Condition") +
  scale_y_continuous(limits = c(0, 1)) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 20),
    axis.title.x = element_text(size = 26),
    axis.title.y = element_text(size = 26),
    axis.text.x = element_text(size = 24),
    axis.text.y = element_text(size = 24),
    legend.text = element_text(size = 24),
    legend.title = element_text(size = 26)
  )


```